---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mgi.report.reader

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/mgi.report.reader)](https://CRAN.R-project.org/package=mgi.report.reader)
[![R-CMD-check](https://github.com/patterninstitute/mgi.report.reader/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/patterninstitute/mgi.report.reader/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`{mgi.report.reader}` provides readers for easy and consistent importing of MGI
(Mouse Genome Informatics) report files:
<https://www.informatics.jax.org/downloads/reports/index.html>.

Essentially, what this package provides is a single function `read_report()`
to import MGI reports. We try to use a consistent naming scheme for variables
across reports, use appropriate variable types, e.g. factors for variables with
small enumerations, convert disparate missing values to `NA`, and other
time-consuming tidying steps, so that you don't have to.

## Installation

``` r
install.packages("mgi.report.reader")
```

## Example

To read an MGI report into R use `read_report()`:

```{r}
library(mgi.report.reader)

base_url <- "https://www.informatics.jax.org/downloads/reports"
marker_list1_rpt <- file.path(base_url, "MRK_List1.rpt")
coordinates_rpt <- file.path(base_url, "MGI_MRK_Coord.rpt")

# Import the Mouse Genetic Markers (including withdrawn marker symbols) Report
read_report(marker_list1_rpt, "MRK_List1", n_max = 10L)
# Import the MGI Marker Coordinates' Report
read_report(coordinates_rpt, "MGI_MRK_Coord", n_max = 10L)
```

## Code of Conduct
  
Please note that the `{mgi.report.reader}` project is released with a [Contributor
Code of Conduct](https://www.pattern.institute/mgi.report.reader/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

## Disclaimer

The `{mgi.report.reader}` package is provided "as is" without any guarantees or
warranty. Although the authors have made every effort to ensure the accuracy and
reliability of the software and its documentation, they are not responsible for
any errors, omissions, or misinterpretations. Users are advised to test the
package thoroughly before relying on it in critical applications. The authors
disclaim all liability for any damage or loss resulting from the use of this
package. Use of the `{mgi.report.reader}` package is at the user's own risk.

## Citing this package

- Firstly, if you use this package please do not forget to start by citing the Mouse Genome Informatics (MGI) and Jackson Laboratory (JAX) as they are the original providers of the data here made accessible with these readers. For details on how to cite MGI resources, please refer to: <https://www.informatics.jax.org/mgihome/other/citation.shtml>.

- To cite us, see <https://www.pattern.institute/mgi.report.reader/authors.html#citation>.
