---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mgi.report.reader

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/mgi.report.reader)](https://CRAN.R-project.org/package=mgi.report.reader)
[![R-CMD-check](https://github.com/patterninstitute/mgi.report.reader/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/patterninstitute/mgi.report.reader/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Overview

The goal of `{mgi.report.reader}` is to facilitate the import of [Mouse Genome
Informatics (MGI)](https://www.informatics.jax.org/downloads/reports/index.html)
report files into R.

## Installation

``` r
install.packages("mgi.report.reader")

# Or the development version from GitHub:
# install.packages("pak")
pak::pak("patterninstitute/mgi.report.reader")
```

## Supported MGI reports

The list of currently supported MGI reports by `{mgi.report.reader}` is provided
by the dataset `reports`:

```{r}
library(mgi.report.reader)

reports
```

## Example

Use `read_report()` to read any supported MGI report into R, e.g. to
read `MRK_List1.rpt`:

```{r}
read_report("marker_list1", n_max = 10L)
```

## Code of Conduct
  
Please note that the `{mgi.report.reader}` project is released with a [Contributor
Code of Conduct](https://www.pattern.institute/mgi.report.reader/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

## Disclaimer

The `{mgi.report.reader}` package is provided "as is" without any guarantees or
warranty. Although the authors have made every effort to ensure the accuracy and
reliability of the software and its documentation, they are not responsible for
any errors, omissions, or misinterpretations. Users are advised to test the
package thoroughly before relying on it in critical applications. The authors
disclaim all liability for any damage or loss resulting from the use of this
package. Use of the `{mgi.report.reader}` package is at the user's own risk.

## Citing this package

- Firstly, if you use this package please do not forget to start by citing the
Mouse Genome Informatics (MGI) and Jackson Laboratory (JAX) as they are the
original providers of the data here made accessible with these readers. For
details on how to cite MGI resources, please refer to:
<https://www.informatics.jax.org/mgihome/other/citation.shtml>.

- To cite us, see <https://www.pattern.institute/mgi.report.reader/authors.html#citation>.
