---
title: "Ensembl, NCBI or MGI Biotype Conflicts"
---

```{r setup, echo=FALSE, message=FALSE}
library(mgi.report.reader)
```

The MGI report `MGI_BioTypeConflict.rpt` provides markers for which
the biotype classification differs across Ensembl, NCBI or MGI. 

To read this report using the key `"biotype_conflicts"`, use the
following code:

```{r}
# To read all records (more than 16,000), use `read_report("ensembl_ids")`.
(biotype_conflicts <- read_report(report_key = "biotype_conflicts", n_max = 30L))
```

Each row is for the combination genetic marker / biotype classification. The
source of the classification is indicated in the `database` variable. The
`gene_id` can be any gene identifier that is meaningful in any of these gene models.

## MGI Representative Gene Model

The variable `is_mgi_rep` stands for _is the MGI genomic representative
sequence_ and is encoded as a logical vector that indicates whether the
corresponding `gene_id` and `biotype` values are the ones associated with MGI
representative sequence. See `vignette("representative_sequence")` for more
details.

```{r}
biotype_conflicts |>
  dplyr::filter(is_mgi_rep)
```

## Variables

### `marker_id`

`marker_id`: `r mgi.report.reader:::desc_marker_id()`

### `marker_symbol`

`marker_symbol`: `r mgi.report.reader:::desc_marker_symbol()`

### `database`

`database`: `r mgi.report.reader:::desc_database()`

### `biotype`

`biotype`: `r mgi.report.reader:::desc_biotype()`

### `gene_id`

`gene_id`: `r mgi.report.reader:::desc_gene_id()`

### `is_mgi_rep`

`is_mgi_rep`: `r mgi.report.reader:::desc_is_mgi_rep()`
