---
title: "GenBank, RefSeq and Ensembl IDs"
---

```{r setup, echo=FALSE, message=FALSE}
library(mgi.report.reader)
```

The MGI report `MRK_Sequence.rpt` provides associations between 
MGI genetic markers and GenBank, RefSeq, Ensembl and UniProtKB identifiers.

To read this report using the key `"genbank_refseq_ensembl_ids"`, use the
following code:

```{r}
# To read all records (more than 70,000), use `read_report("genbank_refseq_ensembl_ids")`.
(assoc_to_seq_ids <- read_report(report_key = "genbank_refseq_ensembl_ids", n_max = 30L))
```

## GenBank, RefSeq, Ensembl and UniProtKB identifiers

These variables hold one or more identifiers associated with each genetic
marker:

- `genbank_id`: GenBank identifier(s)
- `refseq_trp_id`: RefSeq transcript identifier(s)
- `refseq_prt_id`: RefSeq protein identifier(s)
- `ensembl_trp_id`: Ensembl transcript identifier(s)
- `ensembl_prt_id`: Ensembl protein identifier(s)
- `swiss_prt_id`: UniProtKB/Swiss-Prot identifier(s)
- `tr_embl_prt_id`: UniProtKB/TrEMBL identifier(s)
- `unigene_id`: UniGene identifier^[All values are `NA` for this variable.]

Except for `unigene_id`, all these variables are
[list-columns](https://r4ds.hadley.nz/rectangling#list-columns), and provide,
potentially, multiple values for the same genetic marker.

Having these data nested in list-columns offers the convenience of having a
table whose records (rows) correspond to one genetic marker. The downside is
that these multiple identifiers are not readily accessible as they would be if
stored in atomic columns. To unnest them you may use
`tidyr::unnest_longer()`^[To learn more about how to rectangle your hierarchical
(nested) data, see
[Rectangling](https://tidyr.tidyverse.org/articles/rectangle.html).].

Here is an example with marker MGI:1915609, where we unnest Ensembl transcript
identifiers so that we have one per row:

```{r}
assoc_to_seq_ids |>
  dplyr::filter(marker_id == "MGI:1915609") |>
  dplyr::select("marker_id", "marker_symbol", "ensembl_trp_id") |>
  tidyr::unnest("ensembl_trp_id") |>
  print(n = Inf)
```

Note, however, that now the meaning of each row changed: each row is for a
marker / Ensembl transcript combination.

## Variables

### `marker_status`

`marker_status`: `r mgi.report.reader:::desc_marker_status()`

### `marker_type`

`marker_type`: `r mgi.report.reader:::desc_marker_type()`

### `marker_id`

`marker_id`: `r mgi.report.reader:::desc_marker_id()`

### `marker_symbol`

`marker_symbol`: `r mgi.report.reader:::desc_marker_symbol()`

### `marker_name`

`marker_name`: `r mgi.report.reader:::desc_marker_name()`

### `feature_type`

`feature_type`: `r mgi.report.reader:::desc_feature_type()`

### `chromosome`

`chromosome`: `r mgi.report.reader:::desc_chromosome()`

### `start`

`start`: `r mgi.report.reader:::desc_start()`

### `end`

`end`: `r mgi.report.reader:::desc_end()`

### `strand`

`strand`: `r mgi.report.reader:::desc_strand()`

### `genetic_map_pos`

`genetic_map_pos`: `r mgi.report.reader:::desc_genetic_map_pos()`

### `genbank_id`

`genbank_id`: `r mgi.report.reader:::desc_genbank_id()`

### `refseq_trp_id`

`refseq_trp_id`: `r mgi.report.reader:::desc_refseq_trp_id()`

### `refseq_prt_id`

`refseq_prt_id`: `r mgi.report.reader:::desc_refseq_prt_id()`

### `ensembl_trp_id`

`ensembl_trp_id`: `r mgi.report.reader:::desc_ensembl_trp_id()`

### `ensembl_prt_id`

`ensembl_prt_id`: `r mgi.report.reader:::desc_ensembl_prt_id()`

### `swiss_prt_id`

`swiss_prt_id`: `r mgi.report.reader:::desc_swiss_prt_id()`

### `tr_embl_prt_id`

`tr_embl_prt_id`: `r mgi.report.reader:::desc_tr_embl_prt_id()`

### `unigene_id`

`unigene_id`: `r mgi.report.reader:::desc_unigene_id()`
