---
title: "Gene Model Coordinates"
---

```{r setup, echo=FALSE, message=FALSE}
library(mgi.report.reader)
library(dplyr)
```

The MGI report `MGI_Gene_Model_Coord.rpt` lists the subset of mouse genetic
markers that correspond to NCBI and Ensembl gene models.

To read this report using the key `"gene_model_coordinates"`, use the following
code:

```{r}
# To read all records (more than 70,000), use `read_report("gene_model_coordinates")`.
(gene_model_coord <- read_report(report_key = "gene_model_coordinates", n_max = 300L))
```

## NCBI gene model variables

NCBI gene model annotation variables are prefixed with `entrez`:

```{r}
dplyr::select(gene_model_coord, "marker_symbol", dplyr::starts_with("entrez"))
```

## Ensembl gene model variables

Ensembl gene model annotation variables are prefixed with `ensembl`:

```{r}
dplyr::select(gene_model_coord, "marker_symbol", dplyr::starts_with("ensembl"))
```

## Variables

### `marker_type`

`marker_type`: `r mgi.report.reader:::desc_marker_type()`

### `marker_id`

`marker_id`: `r mgi.report.reader:::desc_marker_id()`

### `marker_symbol`

`marker_symbol`: `r mgi.report.reader:::desc_marker_symbol()`

### `marker_name`

`marker_name`: `r mgi.report.reader:::desc_marker_name()`

### `assembly`

`assembly`: `r mgi.report.reader:::desc_assembly()`

### `entrez_gen_id`

`entrez_gen_id`: `r mgi.report.reader:::desc_entrez_gen_id()`

### `entrez_chromosome`

`entrez_chromosome`: `r mgi.report.reader:::desc_entrez_chromosome()`

### `entrez_start`

`entrez_start`: `r mgi.report.reader:::desc_entrez_start()`

### `entrez_end`

`entrez_end`: `r mgi.report.reader:::desc_entrez_end()`

### `entrez_strand`

`entrez_strand`: `r mgi.report.reader:::desc_entrez_strand()`

### `ensembl_gen_id`

`ensembl_gen_id`: `r mgi.report.reader:::desc_ensembl_gen_id()`

### `ensembl_chromosome`

`ensembl_chromosome`: `r mgi.report.reader:::desc_ensembl_chromosome()`

### `ensembl_start`

`ensembl_start`: `r mgi.report.reader:::desc_ensembl_start()`

### `ensembl_end`

`ensembl_end`: `r mgi.report.reader:::desc_ensembl_end()`

### `ensembl_strand`

`ensembl_strand`: `r mgi.report.reader:::desc_ensembl_strand()`
