---
title: "Gene Traps"
---

```{r setup, echo=FALSE, message=FALSE}
library(mgi.report.reader)
```

The MGI report `MRK_GeneTrap.rpt` provides associations between 
MGI genetic markers and gene trap cell lines. For more details about
gene trapping, see MGI's
[Gene Trap Questions and Answers](http://www.informatics.jax.org/userhelp/genetrap_usecase_help.shtml).

To read this report using the key `"gene_trap_ids"`, use the
following code:

```{r}
# To read all records (~ 17,000), use `read_report("gene_trap_ids")`.
(assoc_to_gene_trap_ids <- read_report(report_key = "gene_trap_ids", n_max = 150L))
```

## Gene Trap Cell Lines

The list-column `cell_line_id` provides associated gene trap cell lines. To
unnest `cell_line_id` use:

```{r}
assoc_to_gene_trap_ids |>
  dplyr::select("marker_id", "marker_symbol","cell_line_id") |>
  dplyr::filter(marker_id == "MGI:3698435") |>
  tidyr::unnest("cell_line_id")
```

## Variables

### `marker_status`

`marker_status`: `r mgi.report.reader:::desc_marker_status()`

### `marker_id`

`marker_id`: `r mgi.report.reader:::desc_marker_id()`

### `marker_symbol`

`marker_symbol`: `r mgi.report.reader:::desc_marker_symbol()`

### `marker_name`

`marker_name`: `r mgi.report.reader:::desc_marker_name()`

### `chromosome`

`chromosome`: `r mgi.report.reader:::desc_chromosome()`

### `genetic_map_pos`

`genetic_map_pos`: `r mgi.report.reader:::desc_genetic_map_pos()`

### `cell_line_id`

`cell_line_id`: `r mgi.report.reader:::desc_cell_line_id()`

