---
title: "InterPro Domains"
---

```{r setup, echo=FALSE, message=FALSE}
library(mgi.report.reader)
```

The MGI report `MGI_InterProDomains.rpt` provides associations between 
InterPro domains and MGI genetic markers.

To read this report using the key `"interpro_domains"`, use the
following code:

```{r}
# To read all records (~ 120,000), use `read_report("interpro_domains")`.
(assoc_interpro_domains <- read_report(report_key = "interpro_domains", n_max = 10000L))
```

## Associated MGI markers

To find associated genetic markers with a specific InterPro domain, simply
filter for that domain, e.g. the Retinoid X receptor/HNF4 domain (IPR000003):

```{r}
assoc_interpro_domains |>
  dplyr::filter(interpro_id == "IPR000003")
```

## Associated InterPro domains

For the reverse operation, i.e. finding all associated domains with a genetic
marker, e.g. the gene Rxra:

```{r}
assoc_interpro_domains |>
  dplyr::filter(marker_symbol == "Rxra") |>
  dplyr::select("marker_id", "marker_symbol", "interpro_id", "interpro_domain")
```

Note that these results are not exaustive because we selected the first 10,000
records when importing the report.

## Variables

### `interpro_id`

`interpro_id`: `r mgi.report.reader:::desc_interpro_id()`

### `interpro_domain`

`interpro_domain`: `r mgi.report.reader:::desc_interpro_domain()`

### `marker_id`

`marker_id`: `r mgi.report.reader:::desc_marker_id()`

### `marker_symbol`

`marker_symbol`: `r mgi.report.reader:::desc_marker_symbol()`
