---
title: "Official Genetic Markers"
---

```{r setup, echo=FALSE}
library(mgi.report.reader)
```

The MGI report `MRK_List2.rpt` provides the list of official mouse genetic
markers, i.e. excluding withdrawn marker symbols.

Read this report with key `"marker_list2"`:

```{r}
# To read all records: `read_report("marker_list2")`.
read_report(report_key = "marker_list2", n_max = 10L)
```

Comparatively, the report `MRK_List1.rpt` is for the whole set of genetic
markers, i.e. including withdrawn marker symbols, see `vignette("marker_list1")`
for more details about this other report.

## Variables

### `marker_status`

`marker_status`: `r mgi.report.reader:::desc_marker_status()`

### `marker_type`

`marker_type`: `r mgi.report.reader:::desc_marker_type()`

### `marker_id`

`marker_id`: `r mgi.report.reader:::desc_marker_id()`

### `marker_symbol`

`marker_symbol`: `r mgi.report.reader:::desc_marker_symbol()`

### `marker_name`

`marker_name`: `r mgi.report.reader:::desc_marker_name()`

### `feature_type`

`feature_type`: `r mgi.report.reader:::desc_feature_type()`

### `chromosome`

`chromosome`: `r mgi.report.reader:::desc_chromosome()`

### `start`

`start`: `r mgi.report.reader:::desc_start()`

### `end`

`end`: `r mgi.report.reader:::desc_end()`

### `strand`

`strand`: `r mgi.report.reader:::desc_strand()`

### `genetic_map_pos`

`genetic_map_pos`: `r mgi.report.reader:::desc_genetic_map_pos()`

### `synonyms`

`synonyms`: `r mgi.report.reader:::desc_synonyms()`
