---
title: "All Genetic Markers"
---

```{r setup, echo=FALSE}
library(mgi.report.reader)
```

The MGI report `MRK_List1.rpt` provides the complete list of mouse genetic
markers, including withdrawn marker symbols.

Read this report with key `"marker_list1"`:

```{r}
# To read all records: `read_report("marker_list1")`.
(all_markers <- read_report(report_key = "marker_list1", n_max = 10L))
```

Official, in-use symbols are indicated by the `marker_status` value `"O"`,
whereas withdrawn symbols are indicated with `"W"`.

Comparatively, the report `MRK_List2.rpt` is only for the official genetic
markers, see `vignette("marker_list2")` for more details.

## Old to new marker symbols

If a symbol was withdrawn it is very likely (but not guaranteed) that it is
now replaced by a new MGI identifier and symbol. The variables `marker_id_now`
and `marker_symbol_now` provide these up-to-date values.

```{r}
all_markers |>
  dplyr::select(
    "marker_status",
    "marker_id",
    "marker_id_now",
    "marker_symbol",
    "marker_symbol_now"
  )
```


## Variables

### `marker_status`

`marker_status`: `r mgi.report.reader:::desc_marker_status()`

### `marker_type`

`marker_type`: `r mgi.report.reader:::desc_marker_type()`

### `marker_id`

`marker_id`: `r mgi.report.reader:::desc_marker_id()`

### `marker_symbol`

`marker_symbol`: `r mgi.report.reader:::desc_marker_symbol()`

### `marker_name`

`marker_name`: `r mgi.report.reader:::desc_marker_name()`

### `feature_type`

`feature_type`: `r mgi.report.reader:::desc_feature_type()`

### `chromosome`

`chromosome`: `r mgi.report.reader:::desc_chromosome()`

### `start`

`start`: `r mgi.report.reader:::desc_start()`

### `end`

`end`: `r mgi.report.reader:::desc_end()`

### `strand`

`strand`: `r mgi.report.reader:::desc_strand()`

### `genetic_map_pos`

`genetic_map_pos`: `r mgi.report.reader:::desc_genetic_map_pos()`

### `synonyms`

`synonyms`: `r mgi.report.reader:::desc_synonyms()`

### `marker_id_now`

`marker_id_now`: `r mgi.report.reader:::desc_marker_id_now()`

### `marker_symbol_now`

`marker_symbol_now`: `r mgi.report.reader:::desc_marker_symbol_now()`

### `note`

`note`: `r mgi.report.reader:::desc_note()`



