---
title: "MGI Marker Coordinates"
---

```{r setup, echo=FALSE, message=FALSE}
library(mgi.report.reader)
library(dplyr)
```

The MGI report `MGI_MRK_Coord.rpt` lists mouse genetic markers along with their
genomic annotations, such as chromosome position, genome assembly version, and
the source of the annotation.

To read this report using the key `"marker_coordinates"`, use the following code:

```{r}
# To read all records (more than 600,000), use `read_report("marker_coordinates")`.
(marker_coord <- read_report(report_key = "marker_coordinates", n_max = 300L))
```

For the first 300 records, here is the count by marker type:

```{r}
dplyr::count(marker_coord, marker_type)
```

By chromosome:

```{r}
dplyr::count(marker_coord, chromosome)
```

By annotation source:

```{r}
dplyr::count(marker_coord, source, database)
```

## Variables

### `marker_type`

`marker_type`: `r mgi.report.reader:::desc_marker_type()`

### `marker_id`

`marker_id`: `r mgi.report.reader:::desc_marker_id()`

### `marker_symbol`

`marker_symbol`: `r mgi.report.reader:::desc_marker_symbol()`

### `marker_name`

`marker_name`: `r mgi.report.reader:::desc_marker_name()`

### `feature_type`

`feature_type`: `r mgi.report.reader:::desc_feature_type()`

### `chromosome`

`chromosome`: `r mgi.report.reader:::desc_chromosome()`

### `start`

`start`: `r mgi.report.reader:::desc_start()`

### `end`

`end`: `r mgi.report.reader:::desc_end()`

### `strand`

`strand`: `r mgi.report.reader:::desc_strand()`

### `assembly`

`assembly`: `r mgi.report.reader:::desc_assembly()`

### `source`

`source`: `r mgi.report.reader:::desc_source()`

### `database`

`database`: `r mgi.report.reader:::desc_database()`
