---
title: "Mouse Genetic Markers"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(mgi.report.reader)
library(dplyr)
```

## Introduction

The [MGI (Mouse Genome Informatics)](https://www.informatics.jax.org) provides
three reports under *Mouse Genetic Markers*:

| Name                                                               | File                                                                                           |
|:----------------------------------------|:------------------------------|
| List of Mouse Genetic Markers (including withdrawn marker symbols) | [MRK_List1.rpt](https://www.informatics.jax.org/downloads/reports/MRK_List1.rpt){.uri}         |
| List of Mouse Genetic Markers (excluding withdrawn marker symbols) | [MRK_List2.rpt](https://www.informatics.jax.org/downloads/reports/MRK_List2.rpt){.uri}         |
| MGI Marker Coordinates                                             | [MGI_MRK_Coord.rpt](https://www.informatics.jax.org/downloads/reports/MGI_MRK_Coord.rpt){.uri} |

To read any of these reports into R, you can use the helper `read_report()`, see
the examples below.

## Reports

### Mouse Genetic Markers

Including withdrawn marker symbols:

```{r cache=TRUE}
(base_url <- "https://www.informatics.jax.org/downloads/reports")
(mrk_symbols1 <- read_report(file.path(base_url, "MRK_List1.rpt"), "MRK_List1", n_max = 30L))
```

Note that withdrawn genetic markers are indicated by their `status` being `"W"`
(withdrawn), and `marker_name` typically reads as `"withdrawn, = 2610205H19Rik"`
if there is a more up-to-date symbol.

```{r}
mrk_symbols1 |>
  dplyr::filter(status == "W") |>
  dplyr::select(c("marker_symbol", "marker_name", "marker_type", "status"))
```

Excluding withdrawn marker symbols:

```{r cache=TRUE}
(mrk_symbols2 <- read_report(file.path(base_url, "MRK_List2.rpt"), "MRK_List2", n_max = 10L))
```

### MGI Marker Coordinates

```{r cache=TRUE}
(mrk_coordinates <- read_report(file.path(base_url, "MGI_MRK_Coord.rpt"), "MGI_MRK_Coord", n_max = 10L))
```
