---
title: "Primer Pairs"
---

```{r setup, echo=FALSE, message=FALSE}
library(mgi.report.reader)
```

The MGI report `PRB_PrimerSeq.rpt` provides associations between 
MGI genetic markers and primer pairs (probes^[In MGI, the term _probe_ applies
not only to nucleic acid probes detected, but also to primers for PCR. This
usage is not common outside of MGI.]).

To read this report using the key `"primers"`, use the
following code:

```{r}
# To read all records (more than 45,000), use `read_report("primers")`.
(assoc_primers <- read_report(report_key = "primers", n_max = 30L))
```

## Primer variables

All primer related variables are scoped with the prefix `primer_`. The
`primer_id` variable is the key for a primer pair, which is also a genetic
marker, so it follows the same format as values of `marker_id`.

### Example: `MGI:1923536`

The primer pairs associated with marker MGI:1923536 are:

```{r}
assoc_primers |>
  dplyr::filter(marker_id == "MGI:1923536") |>
  dplyr::select("marker_id", dplyr::starts_with("primer_"))
```

## Variables

### `marker_id`

`marker_id`: `r mgi.report.reader:::desc_marker_id()`

### `marker_symbol`

`marker_symbol`: `r mgi.report.reader:::desc_marker_symbol()`

### `marker_name`

`marker_name`: `r mgi.report.reader:::desc_marker_name()`

### `chromosome`

`chromosome`: `r mgi.report.reader:::desc_chromosome()`

### `genetic_map_pos`

`genetic_map_pos`: `r mgi.report.reader:::desc_genetic_map_pos()`

### `primer_id`

`primer_id`: `r mgi.report.reader:::desc_primer_id()`

### `primer_name`

`primer_name`: `r mgi.report.reader:::desc_primer_name()`

### `primer_fwd_seq`

`primer_fwd_seq`: `r mgi.report.reader:::desc_primer_fwd_seq()`

### `primer_rev_seq`

`primer_rev_seq`: `r mgi.report.reader:::desc_primer_rev_seq()`

### `primer_amplimer_size`

`primer_amplimer_size`: `r mgi.report.reader:::desc_primer_amplimer_size()`
