---
title: "UniProtKB Swiss-Prot"
---

```{r setup, echo=FALSE, message=FALSE}
library(mgi.report.reader)
```

The MGI report `MRK_SwissProt.rpt` provides associations between 
MGI genetic markers and UniProtKB/Swiss-Prot identifiers.

To read this report using the key `"swiss_prot_ids"`, use the
following code:

```{r}
# To read all records (~ 17,000), use `read_report("swiss_prot_ids")`.
(assoc_to_swiss_ids <- read_report(report_key = "swiss_prot_ids", n_max = 150L))
```

## UniProtKB/Swiss-Prot identifiers

The list-column `swiss_prt_id` provides associated ProtKB/Swiss-Prot
identifiers. To unnest `swiss_prt_id` use:

```{r}
assoc_to_swiss_ids |>
  dplyr::select("marker_id", "marker_symbol","swiss_prt_id") |>
  dplyr::filter(marker_id == "MGI:1098687") |>
  tidyr::unnest("swiss_prt_id")
```

## Variables

### `marker_status`

`marker_status`: `r mgi.report.reader:::desc_marker_status()`

### `marker_id`

`marker_id`: `r mgi.report.reader:::desc_marker_id()`

### `marker_symbol`

`marker_symbol`: `r mgi.report.reader:::desc_marker_symbol()`

### `marker_name`

`marker_name`: `r mgi.report.reader:::desc_marker_name()`

### `chromosome`

`chromosome`: `r mgi.report.reader:::desc_chromosome()`

### `genetic_map_pos`

`genetic_map_pos`: `r mgi.report.reader:::desc_genetic_map_pos()`

### `swiss_prt_id`

`swiss_prt_id`: `r mgi.report.reader:::desc_swiss_prt_id()`

