---
title: "UniProtKB Swiss-Prot and TrEMBL"
---

```{r setup, echo=FALSE, message=FALSE}
library(mgi.report.reader)
```

The MGI report `MRK_SwissProt_TrEMBL.rpt` provides associations between 
MGI genetic markers and UniProtKB/Swiss-Prot and UniProtKB/TrEMBL identifiers.

To read this report using the key `"swiss_trembl_ids"`, use the
following code:

```{r}
# To read all records (more than 20,000), use `read_report("swiss_trembl_ids")`.
(assoc_to_swiss_trembl_ids <- read_report(report_key = "swiss_trembl_ids", n_max = 30L))
```

## UniProtKB/Swiss-Prot and UniProtKBTrEMBL identifiers

The list-column `uniprot_id` provides both ProtKB/Swiss-Prot and UniProtKBTrEMBL
identifiers. To unnest `uniprot_id` use:

```{r}
assoc_to_swiss_trembl_ids |>
  dplyr::select("marker_id", "uniprot_id") |>
  dplyr::filter(marker_id == "MGI:1915609") |>
  tidyr::unnest("uniprot_id")
```

## Variables

### `marker_status`

`marker_status`: `r mgi.report.reader:::desc_marker_status()`

### `marker_id`

`marker_id`: `r mgi.report.reader:::desc_marker_id()`

### `marker_symbol`

`marker_symbol`: `r mgi.report.reader:::desc_marker_symbol()`

### `marker_name`

`marker_name`: `r mgi.report.reader:::desc_marker_name()`

### `chromosome`

`chromosome`: `r mgi.report.reader:::desc_chromosome()`

### `genetic_map_pos`

`genetic_map_pos`: `r mgi.report.reader:::desc_genetic_map_pos()`

### `uniprot_id`

`uniprot_id`: `r mgi.report.reader:::desc_uniprot_id()`

